Universal Anonymous Signatures

### 2022-07-04 prism-backend/research/gsac/formal-uas.tex
New proof for non-frameability.
Updated theorem statement for non-frameability of CUASGen.

\begin{figure}[htp!]
  \procedure[linenumbering]{$\ExpNonframe(1^\secpar)$}{%
    (\parm,\trap) \gets \SimSetup(1^\secpar) \\
    (\oid,\siid,\Sig=(\sig,\yeval),\msg,\feval,\yinsp,\iproof) \gets
    \adv^{\Oframe}(\parm) \\
    \pcif \Verify(\PUBOK[\oid],\PUBIK[\siid],\Sig,\msg,\feval) = 0:
    \pcreturn 0 \\
    \pcif \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\Sig,\msg) = 0:
    \pcreturn 0 \\
    (\usk,\scred,\attrs_{\scred},\tyeval^1,\yinsp') \gets
    \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
    \Yeval=(\yeval^0,\yeval^1) \gets \feval(\usk,\scred,\msg) \\
    \pcif \yeval \neq \yeval^0 \lor \tyeval^1 \neq \yeval^1
    \lor \Yeval \notin \rngfeval: \pcreturn 1 \\
    \pcif \finsp(\Yeval,\usk,\scred,\msg) \neq \yinsp
    \lor \yinsp \neq \yinsp': \pcreturn 1 \\    
    \pcif \nexists \uid \in \HU~\suchthat~\UK[\uid] = \usk: \pcreturn 0 \\
    \pcif \nexists (\cdot,\cdot,\Sig,\Yeval,\msg,\feval)
    \in \SIG[\uid]: \pcreturn 1 \\
    \pcreturn 0
  }
  \caption{Experiment for non-frameability on \UAS schemes.}
  \label{fig:exp-uas-frame}
\end{figure}

@@

\begin{theorem}[Non-frameability of \CUASGen]
  \label{thm:frame-uas}
  If the underlying scheme for $\NIZK^{\Issue}$ is zero-knowledge, the schemes
  for $\NIZK^{\Sign}$ are zero-knowledge and simulation-extractable, and the
  commitment scheme is hiding, then our \CUASGen construction satisfies
  non-frameability as defined in \defref{def:frame-uas}, except with negligible
  probability.
\end{theorem}

>>>>

\begin{figure}[htp!]
  \procedure[linenumbering]{$\ExpNonframe(1^\secpar)$}{%
    (\parm,\trap) \gets \SimSetup(1^\secpar) \\
    (\oid,\siid,\Sig=(\sig,\yeval),\msg,\feval,\yinsp,\iproof) \gets
    \adv^{\Oframe}(\parm) \\
    \pcif \Verify(\PUBOK[\oid],\PUBIK[\siid],\Sig,\msg,\feval) = 0:
    \pcreturn 0 \\
    \pcif \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\Sig,\msg) = 0:
    \pcreturn 0 \\
    \pcif \exists (\cdot,\cdot,\Sig,\Yeval,\msg,\feval)
    \in \SIG[\uid]: \pcreturn 0 \\    
    (\usk,\scred,\attrs_{\scred},\tyeval^1,\yinsp') \gets
    \ExtractSign(\trap,\oid,\siid,\Sig,\msg,\feval) \\
    \Yeval=(\yeval^0,\yeval^1) \gets \feval(\usk,\scred,\msg) \\
    \pcif \yeval \neq \yeval^0 \lor \tyeval^1 \neq \yeval^1
    \lor \Yeval \notin \rngfeval: \pcreturn 1 \\
    \pcif \finsp(\Yeval,\usk,\scred,\msg) \neq \yinsp
    \lor \yinsp \neq \yinsp': \pcreturn 1 \\    
    \pcif \exists \uid \in \HU~\suchthat~\UK[\uid] = \usk: \pcreturn 1 \\
    \pcreturn 0
  }
  \caption{Experiment for non-frameability on \UAS schemes.}
  \label{fig:exp-uas-frame}
\end{figure}

@@

\begin{theorem}[Non-frameability of \CUASGen]
  \label{thm:frame-uas}
  If the underlying scheme for $\NIZK^{\Sign}$ is zero-knowledge and simulation
  extractable, the scheme for $\NIZK^{\Open}$ is simulation-extractable, and
  \SBCM scheme is blind, then our \CUASGen construction satisfies
  non-frameability as defined in \defref{def:frame-uas}, except with negligible
  probability.
\end{theorem}
